<!-- Header section -->

<div class = "header-shading">

##### {{question_text}} <br>



</div>



<!-- Body -->


<div class = "anchor">



```{r {{chunk_label}}_descriptives, echo = FALSE}
#########################
# Descriptives
#########################


# Grab basic descriptives
minimum_value <- round(min({{thisVar}}, na.rm = TRUE), 2)
maximum_value <- round(max({{thisVar}}, na.rm = TRUE), 2)
mean_value <- round(mean({{thisVar}}, na.rm = TRUE), 2)
std_value <- round(sd({{thisVar}}, na.rm = TRUE), 2)

```


**Descriptives**
Min = `r minimum_value`, max = `r maximum_value`, mean = `r mean_value`, std = `r std_value`




```{r {{chunk_label}}_library, include = FALSE}
# Library packages
library(kableExtra)
library(ggplot2)
```




<button 
  onclick="let e = document.getElementById('{{chunk_label}}');
           let arrow = document.getElementById('{{chunk_label}}_arrow');
           e.style.display = e.style.display === 'none' ? 'block' : 'none';
           arrow.textContent = e.style.display === 'none' ? '▼' : '▲';"
  style="background: none; border: none; padding: 0; font-weight: bold; font-size: 18px; color: #2a5caa; cursor: pointer;">
Click to view visuals <span id="{{chunk_label}}_arrow">▼</span>
</button>

<div id="{{chunk_label}}" style="display: none;">


<!-- TOC-IGNORE-BEGIN -->

### Descriptives {.tabset}


#### Histogram






```{r {{chunk_label}}_histogram, echo = FALSE}
#################
# This is a basic histogram for continous data
######################
hist({{thisVar}}, main = "Histogram", col ="#619CFF", border = "black", xlab = "0 - 100 Slider", prob = TRUE)

# This line + prob = TRUE arg draws density plot over histogram
lines(density({{thisVar}}, na.rm = TRUE), col="blue", lwd=2)


```


#### Missingness





```{r {{chunk_label}}_missingness, echo = FALSE}
#########################
# Missingness descriptives
########################


# Made-up example stats
minimum_value <- 2
maximum_value <- 18
mean_value <- 7.4
std_value <- 3.6


icc_value <- 0.41  # Made-up value


```

**Missingness Descriptives**

Min = `r minimum_value`, max = `r maximum_value`, mean = `r mean_value`, std = `r std_value`

Interclass Correlation (ICC) = `r icc_value`

**Missingness Codes**

<details>
<summary style="font-weight: bold; font-size: 18px; color: #2a5caa; cursor: pointer;">Click to view missingness codes</summary>

<br>

| Code | Description           |
|------|-----------------------|
| -1   | Skipped by respondent |
| -3   | No response recorded  |
| -6   | Survey timeout        |
| -8   | Consent withdrawn     |
| -9   | Other missing reason  |

</details>







#### Screenshot


</div>

</div>


