<!-- Header section -->

<div class = "header-shading">

### {{question_text}} <br>

<div style="font-weight: bold; color: #2a5caa; margin-top: -0.7em; margin-bottom: 1em;">
  [{{item_id}}]
</div>


</div>



<!-- Body -->


<div class = "anchor">


**Way the question was delivered:** {{question_type}}

**Type of data:** {{result_type}}

```{r, echo = FALSE}
### This is a simple skip logic check
### If this is a conditional question, print out parent item_id and parent question text

# Get current question ID
item_id <- substring("{{item_id}}", 6)


# Change Conditional Child Item ID column to character to make searching easy
blockMap$Conditional.Child.Item.ID <- as.character(blockMap$Conditional.Child.Item.ID)

# Check if Item ID is in conditional column....
## If so, display parent info
if (item_id %in% blockMap$Conditional.Child.Item.ID) {
  parent_row <- subset(blockMap, Conditional.Child.Item.ID == item_id)
  parent_text <- parent_row$Question.Text
  parent_itemID <- parent_row$Item.ID
  cat("This question is only delivered if participant answered question ", parent_itemID, ": ", parent_text)
}




##### I thought the child listed the parent not the other way around
##### This will essentially give you the same in reverse

#if (!is.na(blockMap$Conditional.Child.Item.ID[blockMap$Question.ID == "{{question_id}}"])) {
#  Conditional_itemID <- blockMap$Conditional.Child.Item.ID[blockMap$Question.ID == "{{question_id}}"]
#  Conditional_text <- blockMap$Question.Text[blockMap$Item.ID == Conditional_itemID]
#  cat("This question is only delivered if participant answered question ", Conditional_itemID, ": ", Conditional_text)
#}


```

```{r, echo = FALSE}
#########################
# Descriptives
#########################
thisBlock_df <- thisData[thisData$Question.ID == "{{question_id}}",]
thisBlock_df$User.Response <- as.numeric(thisBlock_df$User.Response)


# Grab basic descriptives
minimum_value <- round(min(thisBlock_df$User.Response, na.rm = TRUE), 2)
maximum_value <- round(max(thisBlock_df$User.Response, na.rm = TRUE), 2)
mean_value <- round(mean(thisBlock_df$User.Response, na.rm = TRUE), 2)
std_value <- round(sd(thisBlock_df$User.Response, na.rm = TRUE), 2)

```


**Descriptives**
Min = `r minimum_value`, max = `r maximum_value`, mean = `r mean_value`, std = `r std_value`


```{r, include = FALSE}
# Library packages
library(kableExtra)
library(ggplot2)
```




<button 
  onclick="let e = document.getElementById('{{item_id}}');
           let arrow = document.getElementById('{{item_id}}_arrow');
           e.style.display = e.style.display === 'none' ? 'block' : 'none';
           arrow.textContent = e.style.display === 'none' ? '▼' : '▲';"
  style="background: none; border: none; padding: 0; font-weight: bold; font-size: 18px; color: #2a5caa; cursor: pointer;">
Click to view visuals <span id="{{item_id}}_arrow">▼</span>
</button>

<div id="{{item_id}}" style="display: none;">


<!-- TOC-IGNORE-BEGIN -->

### Descriptives {.tabset}


#### Histogram





```{r, echo = FALSE}
#################
# This is a basic histogram for continous data
######################
hist(thisBlock_df$User.Response, main = "Histogram", col ="#619CFF", border = "black", xlab = "0 - 100 Slider")


```


#### Missingness





```{r, echo = FALSE}
#########################
# Missingness descriptives
########################


# Made-up example stats
minimum_value <- 2
maximum_value <- 18
mean_value <- 7.4
std_value <- 3.6


icc_value <- 0.41  # Made-up value


```

**Missingness Descriptives**

Min = `r minimum_value`, max = `r maximum_value`, mean = `r mean_value`, std = `r std_value`

Interclass Correlation (ICC) = `r icc_value`

**Missingness Codes**

<details>
<summary style="font-weight: bold; font-size: 18px; color: #2a5caa; cursor: pointer;">Click to view missingness codes</summary>

<br>

| Code | Description           |
|------|-----------------------|
| -1   | Skipped by respondent |
| -3   | No response recorded  |
| -6   | Survey timeout        |
| -8   | Consent withdrawn     |
| -9   | Other missing reason  |

</details>







#### Screenshot


</div>

</div>
