<div class = "anchor">

```{r skip-logic-{{chunk_label}}, echo = FALSE, results = 'asis'}
### This is a simple skip logic check
### If this is a conditional question, print out parent item_id and parent question text

# Get current question ID
item_id_numeric <- substring("{{item_id}}", 6)


# Change Conditional Child Item ID column to character to make searching easy
blockMap$Conditional.Child.Item.ID <- as.character(blockMap$Conditional.Child.Item.ID)

# Check if Item ID is in conditional column....
## If so, display parent info
if (item_id_numeric %in% blockMap$Conditional.Child.Item.ID) {
  parent_row <- subset(blockMap, Conditional.Child.Item.ID == item_id_numeric)
  parent_text <- unique(parent_row$Question.Text)
  parent_itemID <- unique(parent_row$Item.ID)
  
  # Set skip logic to true for easy access
  skipLogic <- TRUE
  
  # Display message
  msg <- paste0(
    "<div style='font-size:16px; line-height:1.5; margin: 1em 0; padding: 0.5em 1em; ",
    "border-left: 4px solid #2a5caa; background-color: #f9faff; color: #333;'>",
    "<strong>Note:</strong> This question is only delivered if participant answered question ",
    "<em>", parent_itemID, "</em>: <em>", parent_text, "</em>.",
    "</div>"
  )
  
  cat(msg)
}




##### I thought the child listed the parent not the other way around
##### This will essentially give you the same in reverse

#if (!is.na(blockMap$Conditional.Child.Item.ID[blockMap$Question.ID == "{{question_id}}"])) {
#  Conditional_itemID <- blockMap$Conditional.Child.Item.ID[blockMap$Question.ID == "{{question_id}}"]
#  Conditional_text <- blockMap$Question.Text[blockMap$Item.ID == Conditional_itemID]
#  cat("This question is only delivered if participant answered question ", Conditional_itemID, ": ", Conditional_text)
#}


```


```{r library-{{chunk_label}}, include = FALSE}
# Library packages
library(kableExtra)
library(ggplot2)
```


<button 
  onclick="let e = document.getElementById('{{question_id}}');
           let arrow = document.getElementById('{{question_id}}_arrow');
           e.style.display = e.style.display === 'none' ? 'block' : 'none';
           arrow.textContent = e.style.display === 'none' ? '▼' : '▲';"
  style="background: none; border: none; padding: 0; font-weight: bold; font-size: 18px; color: #2a5caa; cursor: pointer;">
Click to view visuals <span id="{{question_id}}_arrow">▼</span>
</button>

<div id="{{question_id}}" style="display: none;">


<!-- TOC-IGNORE-BEGIN -->

### Descriptives {.tabset}

#### Frequency Table




```{r frequency-table-{{chunk_label}}, echo = FALSE}

# Check to see that there is data to make a table
if (any(thisData_new$Question.ID == "{{question_id}}") &&
    any(!is.na(thisData_new$User.Response[thisData_new$Question.ID == "{{question_id}}"]))) {
  
  dataExists <- TRUE
  
  # This is a simple frequency table
  multiple_select_table <- table(unlist(strsplit(thisData_new$User.Response[thisData_new$Question.ID == "{{question_id}}"], ",")))
  
  # This gives us the raw counts, ordered for each possible response
  multiple_select_table <- multiple_select_table[order(as.numeric(names(multiple_select_table)))]
  
  # These are the numeric values in the data
  response_indicator <- names(multiple_select_table)
  
  # Make each item a character that is N = *insert count*
  n_counts <- sapply(multiple_select_table, function(x) paste0("N = ", x))
  
  
  
  
  # Next pull out the name labels
  response_labels <- list()
  
  for (i in seq_along(names(multiple_select_table))) {
    val <- as.numeric(names(multiple_select_table)[i])
    response_labels[[i]] <- responseKey_new$definition[responseKey_new$value == val & responseKey_new$Question.ID == "{{question_id}}" & !is.na(responseKey_new$Question.ID) & !is.na(responseKey_new$definition) & !is.na(responseKey_new$value)]
  }
  
  # Unlist 
  response_labels <- unlist(response_labels)
   
  # Grab percentages
  percentages <- round(100 * multiple_select_table / sum(multiple_select_table), 1)
  
  # Make characters
  percentages <- sapply(percentages, function(x) paste0(x, "%"))
  
  
  
  # Combine all into a dataframe
  df <- data.frame(Value = response_indicator, Label = response_labels, Counts = n_counts, Percentages = percentages)
  
  
  
  df %>%
    kbl() %>%
    kable_styling() %>% 
    column_spec(3, color = "darkgreen")

  
  # If no data, make a table with 0's and labels
} else {
  
  dataExists <- FALSE

  
  response_key_subset <- responseKey_new[(responseKey_new$Question.ID == "{{question_id}}" & responseKey_new$type == "Response"), ]
  
  df <- data.frame(
    Value = response_key_subset$value,
    Label = response_key_subset$definition,
    Counts = rep("N = 0", nrow(response_key_subset)),
    Percentages = rep("0%", nrow(response_key_subset))
  )
  
  df %>%
    kbl() %>%
    kable_styling() %>% 
    column_spec(3, color = "darkgreen")
}

```

#### Barplot

```{r barplot-{{chunk_label}}, echo = FALSE}

# Check to make sure the last call made a table
if (dataExists == TRUE) {

  # Convert to data frame dynamically
  df <- data.frame(
    Option = factor(names(multiple_select_table), levels = names(multiple_select_table)),
    Count = as.numeric(multiple_select_table)
  )
  
  # Create ggplot
  ggplot(df, aes(x = Option, y = Count)) +
    geom_bar(stat = "identity", fill = "steelblue") +
    labs(
      title = "{{question_text}}",
      x = "",
      y = ""
    ) +
    theme_minimal()
}
```



#### Missingness



```{r missingness-{{chunk_label}}, echo = FALSE, results = 'asis'}
#########################
# Missingness descriptives
########################

  # Grab amount of times question was delivered / delivered and not answered
    # Grab number of times it was answered
    times_delivered <- nrow(thisData_new[(thisData_new$Question.ID == "{{question_id}}"),])
      
    # Grab number of times it COULD have been answered
    # This is calculated as the amount of times the parent item id was answered with a non NA value
    times_answered <- 
      nrow(thisData_new[(thisData_new$Question.ID == "{{question_id}}" & !is.na(thisData_new$User.Response)),])
    
    # Grab most basic missingness as times could have been answered
    missing <- times_delivered - times_answered


# If skip logic exists..... 
if (exists("skipLogic") && skipLogic == TRUE) {
  
  ###############
  # 1.) Display the amount of people the question was delivered to
  ###############
  
    # Grab the amount of people the question was delivered to
    # This is calculated as the amount of people who responded a non NA value to the parent item
    people_delivered_to <- 
      length(unique(thisData_new$Participant.ID[thisData_new$Question.ID == "{{question_id}}" & !is.na(thisData_new$User.Response)]))
    
    
    # Make message
      # If the question was delivered to everyone...
      if (n == people_delivered_to) {
        delivered_msg <- paste0("This questions was delivered to all ", n, " participants")
        cat(delivered_msg)    
        
      # If the question was NOT delivered to everyone...
      } else {
        delivered_msg <- paste0("This questions was delivered only to ", people_delivered_to, " out of ", n, " participants")
        cat(delivered_msg)          
      }

    
}
 
  
  ###############
  # 3.) Grab missingness descriptives
  ###############    
  
  if (dataExists == TRUE) {  
    
    # Sum the missingness per person
    missing_per_person <- thisData_new %>% 
      filter(Question.ID == "{{question_id}}") %>%
      group_by(Participant.ID) %>% 
      summarize(missingness = sum(is.na(User.Response)))
      
    
    
    # Calculate descriptives
      # Minimum
      missing_minimum_value <- round(min(missing_per_person$missingness, na.rm = TRUE), 2)
      
      # Maximum
      missing_maximum_value <- round(max(missing_per_person$missingness, na.rm = TRUE), 2)
      
      # Mean
      missing_mean_value <- round(mean(missing_per_person$missingness, na.rm = TRUE), 2)
      
      # Standard Deviation
      missing_std_value <- round(sd(missing_per_person$missingness, na.rm = TRUE), 2)
            
      
      # ICC
        # Between person variance
        between_person_variance <- missing_std_value ^ 2
        
        # Within person variance
        p_bar <- times_delivered / times_answered
        within_person_variance <- p_bar * (1 - p_bar)
        # Calculate the ICC
        missing_icc_value <- round(between_person_variance / (between_person_variance + within_person_variance), 2)
 
  # If no data       
  } else {
  missing_minimum_value <- NA
  missing_maximum_value <- NA
  missing_mean_value <- NA
  missing_std_value <- NA
  missing_icc_value <- NA
}


```

**Missingness Descriptives**

Delivered / Answered = `r times_delivered` / `r times_answered`

Missing = `r missing`

Min = `r missing_minimum_value`, max = `r missing_maximum_value`, mean = `r missing_mean_value`, std = `r missing_std_value`
(Descriptives are rounded to 2 decimals)

Missingness Interclass Correlation (ICC) = `r missing_icc_value`


**Missingness Codes**

<details>
<summary style="font-weight: bold; font-size: 18px; color: #2a5caa; cursor: pointer;">Click to view missingness codes</summary>

<br>

| Code | Description           |
|------|-----------------------|
| -1   | Skipped by respondent |
| -3   | No response recorded  |
| -6   | Survey timeout        |
| -8   | Consent withdrawn     |
| -9   | Other missing reason  |

</details>





#### Screenshot



</div>


</div>
