<!-- Header section -->

<div class = "header-shading">

#### {{question_text}} <br>

<div style="font-weight: bold; color: #2a5caa; margin-top: -0.7em; margin-bottom: 1em;">
  [{{item_id}}]
</div>


</div>



<!-- Body -->


<div class = "anchor">

**Question ID**: {{question_id}}

**Way the question was delivered:** {{question_type}}

**Type of data:** {{result_type}}

```{r, include = FALSE}
thisData <- {{thisData}}
responseKey <- {{responseKey}}

```

```{r skip-logic-{{chunk_label}}, echo = FALSE, results = 'asis'}
### This is a simple skip logic check
### If this is a conditional question, print out parent item_id and parent question text

# Get current question ID
item_id_numeric <- substring("{{item_id}}", 6)


# Change Conditional Child Item ID column to character to make searching easy
blockMap$Conditional.Child.Item.ID <- as.character(blockMap$Conditional.Child.Item.ID)

# Check if Item ID is in conditional column....
## If so, display parent info
if (item_id_numeric %in% blockMap$Conditional.Child.Item.ID) {
  parent_row <- subset(blockMap, Conditional.Child.Item.ID == item_id_numeric)
  parent_text <- unique(parent_row$Question.Text)
  parent_itemID <- unique(parent_row$Item.ID)
  
  # Set skip logic to true for easy access
  skipLogic <- TRUE
  
  # Display message
  msg <- paste0(
    "<div style='font-size:16px; line-height:1.5; margin: 1em 0; padding: 0.5em 1em; ",
    "border-left: 4px solid #2a5caa; background-color: #f9faff; color: #333;'>",
    "<strong>Note:</strong> This question is only delivered if participant answered question ",
    "<em>", parent_itemID, "</em>: <em>", parent_text, "</em>.",
    "</div>"
  )
  
  cat(msg)
}




##### I thought the child listed the parent not the other way around
##### This will essentially give you the same in reverse

#if (!is.na(blockMap$Conditional.Child.Item.ID[blockMap$Question.ID == "{{question_id}}"])) {
#  Conditional_itemID <- blockMap$Conditional.Child.Item.ID[blockMap$Question.ID == "{{question_id}}"]
#  Conditional_text <- blockMap$Question.Text[blockMap$Item.ID == Conditional_itemID]
#  cat("This question is only delivered if participant answered question ", Conditional_itemID, ": ", Conditional_text)
#}


```

```{r library-{{chunk_label}}, include = FALSE}
# Library packages
library(kableExtra)
library(ggplot2)
```




<button 
  onclick="let e = document.getElementById('{{question_id}}');
           let arrow = document.getElementById('{{question_id}}_arrow');
           e.style.display = e.style.display === 'none' ? 'block' : 'none';
           arrow.textContent = e.style.display === 'none' ? '▼' : '▲';"
  style="background: none; border: none; padding: 0; font-weight: bold; font-size: 18px; color: #2a5caa; cursor: pointer;">
Click to view visuals <span id="{{question_id}}_arrow">▼</span>
</button>

<div id="{{question_id}}" style="display: none;">


<!-- TOC-IGNORE-BEGIN -->

### Descriptives {.tabset}


#### Missingness



```{r missingness-{{chunk_label}}, echo = FALSE, results = 'asis'}
#########################
# Missingness descriptives
########################

  # Grab amount of times question was delivered / delivered and not answered
    # Grab number of times it was answered
    times_delivered <- nrow(thisData[(thisData$Question.ID == "{{question_id}}"),])
      
    # Grab number of times it COULD have been answered
    # This is calculated as the amount of times the parent item id was answered with a non NA value
    times_answered <- 
      nrow(thisData[(thisData$Question.ID == "{{question_id}}" & !is.na(thisData$User.Response)),])
    
    # Grab most basic missingness as times could have been answered
    missing <- times_delivered - times_answered


# If skip logic exists..... 
if (exists("skipLogic") && skipLogic == TRUE) {
  
  ###############
  # 1.) Display the amount of people the question was delivered to
  ###############
  
    # Grab the amount of people the question was delivered to
    # This is calculated as the amount of people who responded a non NA value to the parent item
    people_delivered_to <- 
      length(unique(thisData$Participant.ID[thisData$Question.ID == "{{question_id}}" & !is.na(thisData$User.Response)]))
    
    
    # Make message
      # If the question was delivered to everyone...
      if (n == people_delivered_to) {
        delivered_msg <- paste0("This questions was delivered to all ", n, " participants")
        cat(delivered_msg)    
        
      # If the question was NOT delivered to everyone...
      } else {
        delivered_msg <- paste0("This questions was delivered only to ", people_delivered_to, " out of ", n, " participants")
        cat(delivered_msg)          
      }

    
}
 
  
  ###############
  # 3.) Grab missingness descriptives
  ###############    
  
  if (dataExists == TRUE) {  
    
    # Sum the missingness per person
    missing_per_person <- thisData %>% 
      filter(Question.ID == "{{question_id}}") %>%
      group_by(Participant.ID) %>% 
      summarize(missingness = sum(is.na(User.Response)))
      
    
    
    # Calculate descriptives
      # Minimum
      missing_minimum_value <- round(min(missing_per_person$missingness, na.rm = TRUE), 2)
      
      # Maximum
      missing_maximum_value <- round(max(missing_per_person$missingness, na.rm = TRUE), 2)
      
      # Mean
      missing_mean_value <- round(mean(missing_per_person$missingness, na.rm = TRUE), 2)
      
      # Standard Deviation
      missing_std_value <- round(sd(missing_per_person$missingness, na.rm = TRUE), 2)
            
      
      # ICC
        # Between person variance
        between_person_variance <- missing_std_value ^ 2
        
        # Within person variance
        p_bar <- times_delivered / times_answered
        within_person_variance <- p_bar * (1 - p_bar)
        # Calculate the ICC
        missing_icc_value <- round(between_person_variance / (between_person_variance + within_person_variance), 2)
 
  # If no data       
  } else {
  missing_minimum_value <- NA
  missing_maximum_value <- NA
  missing_mean_value <- NA
  missing_std_value <- NA
  missing_icc_value <- NA
}


```

**Missingness Descriptives**

Delivered / Answered = `r times_delivered` / `r times_answered`

Missing = `r missing`

Min = `r missing_minimum_value`, max = `r missing_maximum_value`, mean = `r missing_mean_value`, std = `r missing_std_value`
(Descriptives are rounded to 2 decimals)

Missingness Interclass Correlation (ICC) = `r missing_icc_value`


**Missingness Codes**

<details>
<summary style="font-weight: bold; font-size: 18px; color: #2a5caa; cursor: pointer;">Click to view missingness codes</summary>

<br>

| Code | Description           |
|------|-----------------------|
| -1   | Skipped by respondent |
| -3   | No response recorded  |
| -6   | Survey timeout        |
| -8   | Consent withdrawn     |
| -9   | Other missing reason  |

</details>





#### Screenshot



</div>


</div>
